Principle of least action as a software development method

### 2022-11-11 ms.tex
fix

\section{Action and software development}
a. characteristics of the user (e.g. technical capabilities)
b. characteristics of the user environment (e.g. Operating system)
c. characteristics of the developer (e.g. technical capabilities)
choose the technologies that allow the developer to minimize the development and user path length through space (other computers) and time (in the future)
d. characteristics of the developer environment (e.g. Operating system)
different stakeholders calculate different actions. the developer sees the path that corresponds to the development procedure while the user sees the path that corresponds the usage of the binary
if the benefit is greater than the cost then it is implemented
moreover the cost and benefits are relative to the user and developer respectively
software development should take in consideration stability both for the user and the developer across two axis: space (other machines) and time
stability not only applies the same program use but also to other programs
the benefit of achieving a target is balanced with the cost of the time required to achieve it
the minimal action principle results in the unix philosophy: Programs should do one thing and one thing only. From that sense a window manager should only be responsible for managing windows and not workspaces, tags etc
the central concept of the paper is translating the idea of action and the principle of minimal action to software development as a specification and then show the implementation that uses Makefile+containers
present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
creating a program (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
the target is the the final program which can be reached with make. The target should fulfill the needs of the users and can change
both users and developers want to reduce their relative action. Balance is achieved at a point
The principle of least action can be used throughout all decision of a software project.

@@

>>>>

\section{Action and software development}
The principle of least action can be used throughout all decision of a software project.

a. characteristics of the user (e.g. technical capabilities)
b. characteristics of the user environment (e.g. Operating system)
c. characteristics of the developer (e.g. technical capabilities)
choose the technologies that allow the developer to minimize the development and user path length through space (other computers) and time (in the future)
d. characteristics of the developer environment (e.g. Operating system)
different stakeholders calculate different actions. the developer sees the path that corresponds to the development procedure while the user sees the path that corresponds the usage of the binary
if the benefit is greater than the cost then it is implemented
moreover the cost and benefits are relative to the user and developer respectively
software development should take in consideration stability both for the user and the developer across two axis: space (other machines) and time
stability not only applies the same program use but also to other programs
the benefit of achieving a target is balanced with the cost of the time required to achieve it
the minimal action principle results in the unix philosophy: Programs should do one thing and one thing only. From that sense a window manager should only be responsible for managing windows and not workspaces, tags etc
the central concept of the paper is translating the idea of action and the principle of minimal action to software development as a specification and then show the implementation that uses Makefile+containers
present the design and implementation of fswm, then the Makefile for python and tex for document generation and then the Makefile for website creation
creating a program (the target) sometimes requires creating tools (as intermediate targets) that can be use to reduce the development time (the path length to the target)
it is not just about minimizing time or being completely accurate in satisfying the requirements. A combination of these is required
the path to the target is the source code which can be evaluated with make check. The path should fulfill the needs of the developers and can change
the target is the the final program which can be reached with make. The target should fulfill the needs of the users and can change
both users and developers want to reduce their relative action. Balance is achieved at a point

@@

\section{Various}
semantic html is a standard. And standards should be used if no personal opinion is required in the subject.
